Interactive dashboard to monitor the COVID-19 outbreak

### 2022-04-20 manuscript_covid19dashboard.Rmd
Working on the methodology section

We obtained data from COVID-19 situation reports published by Epidemiology Unit, Ministry of Health Sri Lanka. We obtained data corresponds to number of death cases, number of reported cases, number of recovered cases and COVID-19 vaccinated counts in Sri Lanka. The data are made available through an open-source R package covid19srilanka [@talagala].

@@

R software was used for data cleaning and analysis. The flexdashboard [@flexdashboard] package was used to build the data visualization dashboard.

@@

@@

**Table 05: Description of the panels**

>>>>

We obtained data from COVID-19 situation reports published by Epidemiology Unit, Ministry of Health Sri Lanka. We obtained data corresponds to number of death cases, number of hospitalized cases, number of recovered cases and COVID-19 vaccinated counts in Sri Lanka. The data are made available through an open-source R package covid19srilanka [@talagala].

@@

R software was used for data cleaning and analysis. The flexdashboard [@flexdashboard] package was used to build the data visualization dashboard. The initial layout for the dashboard was prepared based on @rami.

@@

Table 5 provides an overview of methods that have been used to visualize data.

**Table 5: Data visualization approaches used to visualize data**

| **Data**|**Type of graphics**| 
|:-------------------|:----------------|
|Daily COVID-19 confirmed          |Time series plots \hfill\break
|Daily COVID-19 recovered cases by time         |Time series plots \hfill\break
|Daily COVID-19 death cases by time         |Time series plots \hfill\break
|Total COVID-19 confirmed cases by time and wave         |Time series plots annotated with vertical lines to denote significant milestones \hfill\break
|Total COVID-19 death cases by time and wave         | Histogram \hfill\break
|Distribution of COVID-19 patients by districts        | Tile map, Choropleth maps, Dorling Cartogram, heatmaps \hfill\break
|Total vaccination by first dose and second dose        | Time series plot \hfill\break
|Total administrated does by vaccine name       | Stacked bar chart \hfill\break
|Total administrated does by vaccine name       | Stacked bar chart \hfill\break
|Total administrated does by vaccine name       | Stacked bar chart \hfill\break

@@

**Table 6: Description of the panels**

### 2022-04-20 manuscript_covid19dashboard.tex
Working on the methodology section

We obtained data from COVID-19 situation reports published by
Epidemiology Unit, Ministry of Health Sri Lanka. We obtained data
corresponds to number of death cases, number of reported cases, number
of recovered cases and COVID-19 vaccinated counts in Sri Lanka. The data
are made available through an open-source R package covid19srilanka
(Talagala 2021).

@@

R software was used for data cleaning and analysis. The flexdashboard
(Iannone, Allaire, and Borges 2020) package was used to build the data
visualization dashboard.

@@

@@

\textbf{Table 05: Description of the panels}

@@

>>>>

We obtained data from COVID-19 situation reports published by
Epidemiology Unit, Ministry of Health Sri Lanka. We obtained data
corresponds to number of death cases, number of hospitalized cases,
number of recovered cases and COVID-19 vaccinated counts in Sri Lanka.
The data are made available through an open-source R package
covid19srilanka (Talagala 2021).

@@

R software was used for data cleaning and analysis. The flexdashboard
(Iannone, Allaire, and Borges 2020) package was used to build the data
visualization dashboard. The initial layout for the dashboard was
prepared based on Krispin (2021).

@@

Table 5 provides an overview of methods that have been used to visualize
data.

\textbf{Table 5: Data visualization approaches used to visualize data}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.54}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.46}}@{}}
\toprule
\textbf{Data} & \textbf{Type of graphics} \\
\midrule
\endhead
Daily COVID-19 confirmed & Time series plots \hfill\break \\
Daily COVID-19 recovered cases by time & Time series plots
\hfill\break \\
Daily COVID-19 death cases by time & Time series plots \hfill\break \\
Total COVID-19 confirmed cases by time and wave & Time series plots
annotated with vertical lines to denote significant milestones
\hfill\break \\
Total COVID-19 death cases by time and wave & Histogram \hfill\break \\
Distribution of COVID-19 patients by districts & Tile map, Choropleth
maps, Dorling Cartogram, heatmaps \hfill\break \\
Total vaccination by first dose and second dose & Time series plot
\hfill\break \\
Total administrated does by vaccine name & Stacked bar chart
\hfill\break \\
Total administrated does by vaccine name & Stacked bar chart
\hfill\break \\
Total administrated does by vaccine name & Stacked bar chart
\hfill\break \\
\bottomrule
\end{longtable}

@@

\textbf{Table 6: Description of the panels}

@@

\leavevmode\hypertarget{ref-rami}{}%
Krispin, Rami. 2021. {``{The Coronavirus Dashboard}.''}
\url{https://github.com/RamiKrispin/coronavirus_dashboard}.
